State of the Practice for Lattice Boltzmann Method Software

### 2022-01-05 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Further divided practices to have a separate list of those that are recommended, but not mentioned by LBM developers or present in their projects

\begin{itemize}
	\item Include OS compatibility, including specific OS versions. This was
	done by several top ranked packages, including ESPResSo and LUMA.
	\item Provide complete installation instructions. This was done by all of
	the top five ranked packages.
	\item Installation instructions should be written as if the user does not
	have any dependencies installed and is installing on a clean OS. This was
	done by several top ranked packages, including ESPResSo, OpenLB, and
	Palabos. This can be tested on a clean environment using a virtual machine.
	\item List all dependencies in the installation instructions, dependency
	versions, and how to install them. This was done by several top ranked
	packages, including ESPResSo, LUMA, OpenLB, and Palabos.
	\item If possible, automate the installation of dependencies. Use tools such
	as Make. This was done by all of the top five ranked packages.
	\item Automate the installation process as much as possible. Use tools such
	as Make. This was done by all of the top five ranked packages.
	\item The installation instruction should only be in one location. This was
	done by several top ranked packages, including ESPResSo, OpenLB, and
	Palabos.
	\item Include descriptive error messages for errors encountered during
	installation. This was done by several top ranked packages, including Ludwig
	and LUMA.
	\item Provide a way to validate the installation. This can be done using a
	custom script, or a test case that specifies expected output. This was done
	by several top ranked packages, including OpenLB, Ludwig, LUMA, and Palabos.
	\item Provide instructions for uninstalling the software. These were
	included with pyLBM.
\end{itemize}

\subsubsection{Surface Correctness and Verifiability}

\begin{itemize}
	\item Use a requirements specification document. This is suggested in SCS
	literature, and several of the top ranked packages had such a document or
	reference to theory manuals. A potential template is presented in
	\citep{smith2005new}. 
	\item Make public (on package website or GitHub) the requirements
	specification document, or explicitly reference the domain theory that the
	software is designed from.  This was done by several top ranked packages,
	including ESPResSo, Ludwig, LUMA, and OpenLB.
	\item Ensure the above information is easy to find. Consider adding it to
	the user manual. The information is easy to find in most top ranked
	packages.
	\item Development teams should include both domain experts and experienced
	software developers. This suggestion is based on developer comments.
	\item Use and make public (on package website or GitHub) detailed
	documentation. Consider using automatic document generation tools like
	Doxygen, Drasil, or Sphinx. This was done by all of the top five ranked
	packages.
	\item Provide detailed tutorials that include expected output, like the
	\href{https://www.walberla.net/doxygen/index.html}{waLBerla tutorials}.
	\item Use unit tests during development and make them public (on package
	website or GitHub). This was available for Ludwig.
	\item Modularize the source code, separate components, hide information
	behind well defined interfaces. This is suggested in SCS literature, and in
	developer comments.  \wss{one of Wilson's best practices.}
	\item Use continuous integration tools (Bamboo, Jenkins, and Travis CI) and
	processes during development. This was done by top ranked packages ESPResSo
	and Ludwig.  \wss{Common in LBM - more common than in other domains}
\end{itemize}

\subsubsection{Surface Reliability}

\begin{itemize}
	\item Include descriptive error messages where appropriate. This was done by
	most packages that encountered a fault.
	\item In case automatic installation of dependencies fails, the system
	should indicate to the user what dependencies need to be installed manually.
	This was done by many packages, including ESPResSo++, Ludwig, LUMA, pyLBM,
	TCLB.
	\item The packages should include detailed tutorials, including
	dependencies, expected output, and any additional supplementary
	documentation that may be required. This was done by many packages,
	including waLBerla, Palabos, MechSys, LUMA, and pyLBM.  \wss{Comment from
	ASCR attendee that success with open source requires good tutorials and
	documentation - is this published anywhere?}
\end{itemize}

\subsubsection{Surface Robustness}

\begin{itemize}
	\item The system must provide descriptive error messages when it encounters
	unexpected input, including incorrect data types, empty input, and missing
	files or links. Nineteen of the software packages behaved reasonably when
	tested with unexpected input.
\end{itemize}

\subsubsection{Surface Performance}

\begin{itemize}
	\item Integrate parallelization tools and techniques to reduce processing
	time. Consider GPU processing, CUDA, and MPI. Eighteen software packages
	mentioned parallelization in their artifacts.
	\item The user should be able to choose to process their model on either the
	CPU or GPU. ESPResSo, lbmpy, lettuce, pyLBM, and TCLB allow for either CPU
	or GPU processing.
\end{itemize}

\subsubsection{Surface Usability}

\begin{itemize}
	\item Include user hardware and software requirements documentation.
	Hardware requirements are rarely listed in the software packages that were
	assessed. Only those offering GPU processing (ESPResSo, lbmpy, lettuce,
	pyLBM, Sailfish, TCLB) mentioned any hardware requirements. On the other
	hand, some sort of software requirements were available for all packages,
	even if only some dependencies or a compatible operating system were
	mentioned.
	\item Provide a user tutorial that indicates the expected output. This was
	done by many packages, including waLBerla, Palabos, MechSys, LUMA, pyLBM.
	\item Provide a detailed user manual. It should identify elements of user
	interfaces, and identify all requirements to model a system. Thirteen
	packages have a user manual. ESPResSo has a well detailed manual.
	\item State appropriate fluid dynamics problems that the software is
	designed to model in the documentation, and explicitly state the limits of
	the software. This is done in the ESPResSo user guide.
	\item Provide documentation that details the background theory information,
	or provide a reference to such information. This was done by several top
	ranked packages, including ESPResSo, Ludwig, LUMA, and OpenLB.
	\item Identify expected user characteristics. LIMBES, Ludwig, laboetie, and
	Palabos did this. The importance of specifying user characteristics is
	discussed in \citep{smith2007requirements}.
	\item Keep all documentation in one location. This was done by top ranked
	packages.
	\item Do not duplicate artifact information. This is suggested as good
	software development practice. Duplicate information is difficult to
	maintain. 
	\item Maintain a user support model (Git, email, forum, FAQ). This was done
	by all of the top five ranked packages.
	\item If possible, consider using popular user-friendly software languages
	like Python. Especially consider this for parts of the source code that is
	likely to be modified or reviewed by users. ESPResSo and Sailfish use Python
	to shorten development time and improve usability.
\end{itemize}

\begin{itemize}
	\item Keep artifacts updated. This is suggested as good software maintenance
	practice.
	\item Ideally include most of the common and less common artifacts listed in
	Section~\ref{artifacts}.
	\item Include version numbers and release notes for all major source code
	and artifact releases. The top five ranked software packages include release
	notes.
	\item Have a defined process for accepting contributions, and make public
	documentation for making contributions to the project. The top five ranked
	software packages include information on how to contribute. 
	\item Use an issue tracker (Git, email, SourceForge, other) to manage bugs
	and changes. Issues should be regularly reviewed and closed. All but three
	(laboetie, lettuce, Sailfish) of the software packages that use Git have
	most of their issues closed.
	\item Use a version control system (GitHub, CVS). Four (ESPREsSo, Ludwig,
	LUMA, Palabos) of the top five ranked packages use a version control system.
	\item Source code needs to be well commented. Typically, more than 10
	percent of LBM package source code is comments, as presented in
	Table~\ref{gitrepodata}. Four of the top five overall ranked packages
	(Ludwig, ESPResSo, Palabos, OpenLB) have about 20 percent of their source
	code as comments.
	\item Modularize the source code, separate components, hide information
	behind well defined interfaces. This is suggested in SCS literature, and in
	developer comments.
	\item Eliminate code duplication. This is suggested as good software
	development practice. Duplicate code is difficult to maintain. \wss{No
	support for this one or citation, either find or remove it.}
	\item If possible, consider using popular user-friendly software languages
	like Python. Especially consider this for parts of the source code that is
	likely to be modified or reviewed by users. ESPResSo and Sailfish use Python
	to address several software qualities, including maintainability.
	\item Consider the recommended points for addressing traceability.
\end{itemize}

\begin{itemize}
	\item Modularize the source code, separate components, hide information
	behind well defined interfaces. This is suggested in SCS literature, and in
	developer comments.  \wss{add citation - Wilson mentions - this points seems
	repetitive}
	\item Consider future source code modifiability as early as the design stage
	of development. This is suggested as good software development practice.
	\wss{citation, support, or remove.}
	\item Consider flexibility of data structures and data storage in the design
	stage. The package pyLBM redeveloped data structures to ease future changes.
\end{itemize}

\begin{itemize}
	\item Modularize the source code, separate components, hide information
	behind well defined interfaces. This is suggested in SCS literature, and in
	developer comments.  \wss{repeated from elsewhere - there should be an
	easier way to do this - give the advice and then link it to the qualities,
	instead of this way?}
	\item Document module interfaces in design and developer documentation. This
	is suggested as good software development practice. \wss{citation or support}
	\item Provide API documentation, if applicable. Only one (ESPResSo) of the
	top five ranked packages provided API documentation.
\end{itemize}

\subsubsection{Surface Understandability}

\begin{itemize}
	\item Adopt a coding standard and document it in artifacts, including some
	examples. A coding standard needs to be part of continuous integration. Only
	LUMA, HemeLB, and Musubi explicitly identify coding standards. 
	\item Use consistent, distinctive, and meaningful code identifiers. Twenty
	of the 24 software packages use such code identifiers.
	\item Use symbolic constants. Thirteen of the 24 software packages use such
	constants.
	\item Identify algorithms that are used in source code comments. Document
	them in the artifacts. Cite relevant external sources if needed. Domain
	algorithms are noted in the source code of 11 packages.
	\item Add meaningful comments. Indicate what is being done in each section
	of source code. All of the top ranked packages have meaningful comments in
	their source code.
	\item Modularize the source code, separate components, hide information
	behind well defined interfaces. This is suggested in SCS literature, and in
	developer comments. \wss{repetitive}
	\item Provide a user manual that identifies all technical and problem
	modeling requirements. Thirteen software packages have a user manual.
	\item State appropriate fluid dynamics problems that the software is
	designed to model in the documentation, and explicitly state the limits of
	the software. This is done in the ESPResSo user guide. 
	\item Consider adding a FAQ section to the documentation. This helped
	resolve some usability issues for OpenLB.
	\item \wss{This quality is basically going through the list of things that
	were measured by the template.}
\end{itemize}

\begin{itemize}
	\item Update all relevant documentation when a change to the software is
	made. This is suggested as good software development practice.
	\wss{support, cite or remove}
	\item Use automatic document generation tools (Doxygen, Drasil, Sphinx) to
	limit the time spent on updating documentation. This was done by all of the
	top five ranked packages. \wss{repetitive}
	\item Provide a developer's guide to help orient developers to the
	artifacts, source code, and system architecture so that they can better
	document changes. Top ranked package OpenLB has a developer guide. \wss{How
	is this related to traceability?}
\end{itemize}

\begin{itemize}
	\item Summarize the development process that is used. Provide information on
	how new users can contribute. Identify the development model by name
	(waterfall, agile, etc.), if appropriate.  Seven of the software packages
	have some artifacts outlining the general development process. Eleven
	packages have information on how to contribute. 
	\item Identify the development environment. Eight of the 24 software
	packages identify the development environment.
	\item Update all relevant documentation when a change to the software is
	made. This is suggested as good software development practice.
	\item Include notes with all releases. Nine of the packages include release notes.
	\item Communicate all changes within the development team. This suggestion
	is based on developer comments.
	\item Use continuous integration processes and tools (Bamboo, Jenkins, and
	Travis CI). This was done by top ranked packages ESPResSo and Ludwig.
	\item Consider peer review processes to assess contributions and ensure the
	tracking of information. High ranked package ESPResSo uses a peer review
	process for contributions. 
	\item Use project management tools, including change and version control
	tools (GitHub, GitLab, CVS), collaboration tools (GitHub, GitLab), and
	document generation tools (Doxygen, Drasil, Sphinx). This was done by all of
	the top five ranked packages. \wss{repetitive}
\end{itemize}

\begin{itemize}
	\item Test output against automatically calculated or known correct results.
	High ranked package ESPResSo does this.
	\item Automate the testing of output. Run tests after all code changes. High
	ranked package ESPResSo does this.
	\item Consider peer review processes and task based inspection to assess
	contributions. High ranked package ESPResSo does this.
	\item Update all relevant design documentation when a change to the software
	is made. This is suggested as good software development practice.
	\wss{cite, support, or remove}
\end{itemize}

\begin{itemize}
	\item Documentation must state all technical requirements and software
	dependencies. A missing dependency was a frequent cause of fault conditions
	during this assessment.
	\item Provide a detailed user manual. Thirteen packages have a user manual.
	ESPResSo has a well detailed manual.
	\item Provide a table of symbols in the developer's guide that maps to names
	used in the source code. This is suggested as good software development
	practice.
	\item State appropriate fluid dynamics problems that the software is
	designed to model in the documentation, and explicitly state the limits of
	the software. This is done in the ESPResSo user guide.
	\item The documentation should either explain the underlying CFD theories or
	provide a reference to appropriate resources. This was done by several top
	ranked packages, including ESPResSo, Ludwig, LUMA, and OpenLB.
	\item Consider asking users for feedback on the documentation. The developer
	of pyLBM noted that such feedback would be appreciated.
\end{itemize}

@@

practices mentioned in literature, but not practiced (if any)

>>>>

\begin{itemize}
	\item Surface Reliability. Include descriptive error messages where
	appropriate. This was done by most packages that encountered a fault.
	\item Surface Reliability. In case automatic installation of dependencies
	fails, the system should indicate to the user what dependencies need to be
	installed manually. This was done by many packages, including ESPResSo++,
	Ludwig, LUMA, pyLBM, TCLB.
	\item Surface Reliability. The packages should include detailed tutorials,
	including dependencies, expected output, and any additional supplementary
	documentation that may be required. This was done by many packages,
	including waLBerla, Palabos, MechSys, LUMA, and pyLBM.  \wss{Comment from
	ASCR attendee that success with open source requires good tutorials and
	documentation - is this published anywhere?}
	\item Surface Robustness. The system must provide descriptive error messages
	when it encounters unexpected input, including incorrect data types, empty
	input, and missing files or links. Nineteen of the software packages behaved
	reasonably when tested with unexpected input.
	\item Surface Performance. Integrate parallelization tools and techniques to
	reduce processing time. Consider GPU processing, CUDA, and MPI. Eighteen
	software packages mentioned parallelization in their artifacts.
	\item Surface Performance. The user should be able to choose to process
	their model on either the CPU or GPU. ESPResSo, lbmpy, lettuce, pyLBM, and
	TCLB allow for either CPU or GPU processing.
	\item Surface Usability. Include user hardware and software requirements
	documentation. Hardware requirements are rarely listed in the software
	packages that were assessed. Only those offering GPU processing (ESPResSo,
	lbmpy, lettuce, pyLBM, Sailfish, TCLB) mentioned any hardware requirements.
	On the other hand, some sort of software requirements were available for all
	packages, even if only some dependencies or a compatible operating system
	were mentioned.
	\item Surface Usability. Provide a user tutorial that indicates the expected
	output. This was done by many packages, including waLBerla, Palabos,
	MechSys, LUMA, pyLBM.
	\item Surface Usability. Provide a detailed user manual. It should identify
	elements of user interfaces, and identify all requirements to model a
	system. Thirteen packages have a user manual. ESPResSo has a well detailed
	manual.
	\item Maintainability. Ideally include most of the common and less common
	artifacts listed in Section~\ref{artifacts}.
	\item Surface Understandability. Use consistent, distinctive, and meaningful
	code identifiers. Twenty of the 24 software packages use such code
	identifiers.
	\item Surface Understandability. Use symbolic constants. Thirteen of the 24
	software packages use such constants.
	\item Surface Understandability. Identify algorithms that are used in source
	code comments. Document them in the artifacts. Cite relevant external
	sources if needed. Domain algorithms are noted in the source code of 11
	packages.
	\item Surface Understandability. Provide a user manual that identifies all
	technical and problem modeling requirements. Thirteen software packages have
	a user manual.
	\item Unambiguity. Provide a detailed user manual. Thirteen packages have a
	user manual. ESPResSo has a well detailed manual.

\end{itemize}

@@

\begin{itemize}
	\item Installability. Include OS compatibility, including specific OS
	versions. This was done by several top ranked packages, including ESPResSo
	and LUMA.
	\item Installability. Provide complete installation instructions. This was
	done by all of the top five ranked packages.
	\item Installability. Installation instructions should be written as if the
	user does not have any dependencies installed and is installing on a clean
	OS. This was done by several top ranked packages, including ESPResSo,
	OpenLB, and Palabos. This can be tested on a clean environment using a
	virtual machine.
	\item Installability. List all dependencies in the installation
	instructions, dependency versions, and how to install them. This was done by
	several top ranked packages, including ESPResSo, LUMA, OpenLB, and Palabos.
	\item Installability. If possible, automate the installation of
	dependencies. Use tools such as Make. This was done by all of the top five
	ranked packages.
	\item Installability. Automate the installation process as much as possible.
	Use tools such as Make. This was done by all of the top five ranked
	packages.
	\item Installability. The installation instruction should only be in one
	location. This was done by several top ranked packages, including ESPResSo,
	OpenLB, and Palabos.
	\item Installability. Include descriptive error messages for errors
	encountered during installation. This was done by several top ranked
	packages, including Ludwig and LUMA.
	\item Installability. Provide a way to validate the installation. This can
	be done using a custom script, or a test case that specifies expected
	output. This was done by several top ranked packages, including OpenLB,
	Ludwig, LUMA, and Palabos.
	\item Installability. Provide instructions for uninstalling the software.
	These were included with pyLBM.
	\item Surface Correctness and Verifiability. Make public (on package website
	or GitHub) the requirements specification document, or explicitly reference
	the domain theory that the software is designed from.  This was done by
	several top ranked packages, including ESPResSo, Ludwig, LUMA, and OpenLB.
	\item Surface Correctness and Verifiability. Ensure the above information is
	easy to find. Consider adding it to the user manual. The information is easy
	to find in most top ranked packages.
	\item Surface Correctness and Verifiability. Development teams should
	include both domain experts and experienced software developers. This
	suggestion is based on developer comments.
	\item Surface Correctness and Verifiability. Traceability. Visibility and Transparency. Use and make public (on package
	website or GitHub) detailed documentation. Consider using automatic document
	generation tools like Doxygen, Drasil, or Sphinx. This was done by all of
	the top five ranked packages.
	\item Surface Correctness and Verifiability. Provide detailed tutorials that
	include expected output, like the
	\href{https://www.walberla.net/doxygen/index.html}{waLBerla tutorials}.
	\item Surface Correctness and Verifiability. Use unit tests during
	development and make them public (on package website or GitHub). This was
	available for Ludwig.
	\item Surface Correctness and Verifiability. Modularize the source code,
	separate components, hide information behind well defined interfaces. This
	is suggested in SCS literature, and in developer comments.  \wss{one of
	Wilson's best practices.}
	\item Surface Understandability. Maintainability.  Modifiability.
	Reusability. Modularize the source code, separate components, hide
	information behind well defined interfaces. This is suggested in SCS
	literature, and in developer comments. \wss{add citation - Wilson mentions -
	this points seems repetitive}
	\item Surface Correctness and Verifiability. Use continuous integration
	tools (Bamboo, Jenkins, and Travis CI) and processes during development.
	This was done by top ranked packages ESPResSo and Ludwig.  \wss{Common in
	LBM - more common than in other domains}
	\item Surface Usability. State appropriate fluid dynamics problems that the
	software is designed to model in the documentation, and explicitly state the
	limits of the software. This is done in the ESPResSo user guide.
	\item Surface Usability. Provide documentation that details the background
	theory information, or provide a reference to such information. This was
	done by several top ranked packages, including ESPResSo, Ludwig, LUMA, and
	OpenLB.
	\item Surface Usability. Identify expected user characteristics. LIMBES,
	Ludwig, laboetie, and Palabos did this. The importance of specifying user
	characteristics is discussed in \citep{smith2007requirements}.
	\item Surface Usability. Keep all documentation in one location. This was
	done by top ranked packages.
	\item Surface Usability. Maintain a user support model (Git, email, forum,
	FAQ). This was done by all of the top five ranked packages.
	\item Surface Usability. If possible, consider using popular user-friendly
	software languages like Python. Especially consider this for parts of the
	source code that is likely to be modified or reviewed by users. ESPResSo and
	Sailfish use Python to shorten development time and improve usability.
	\item Maintainability. Include version numbers and release notes for all
	major source code and artifact releases. The top five ranked software
	packages include release notes.
	\item Maintainability. Have a defined process for accepting contributions,
	and make public documentation for making contributions to the project. The
	top five ranked software packages include information on how to contribute. 
	\item Maintainability. Use an issue tracker (Git, email, SourceForge, other)
	to manage bugs and changes. Issues should be regularly reviewed and closed.
	All but three (laboetie, lettuce, Sailfish) of the software packages that
	use Git have most of their issues closed.
	\item Maintainability. Use a version control system (GitHub, CVS). Four
	(ESPREsSo, Ludwig, LUMA, Palabos) of the top five ranked packages use a
	version control system.
	\item Maintainability. Source code needs to be well commented. Typically,
	more than 10 percent of LBM package source code is comments, as presented in
	Table~\ref{gitrepodata}. Four of the top five overall ranked packages
	(Ludwig, ESPResSo, Palabos, OpenLB) have about 20 percent of their source
	code as comments.
	\item Maintainability. If possible, consider using popular user-friendly
	software languages like Python. Especially consider this for parts of the
	source code that is likely to be modified or reviewed by users. ESPResSo and
	Sailfish use Python to address several software qualities, including
	maintainability.
	\item Modifiability. Consider flexibility of data structures and data
	storage in the design stage. The package pyLBM redeveloped data structures
	to ease future changes.
	\item Reusability. Provide API documentation, if applicable. Only one
	(ESPResSo) of the top five ranked packages provided API documentation.
	\item Surface Understandability. Adopt a coding standard and document it in
	artifacts, including some examples. A coding standard needs to be part of
	continuous integration. Only LUMA, HemeLB, and Musubi explicitly identify
	coding standards. 
	\item Surface Understandability. Add meaningful comments. Indicate what is
	being done in each section of source code. All of the top ranked packages
	have meaningful comments in their source code.
	\item Surface Understandability. State appropriate fluid dynamics problems
	that the software is designed to model in the documentation, and explicitly
	state the limits of the software. This is done in the ESPResSo user guide. 
	\item Surface Understandability. Consider adding a FAQ section to the
	documentation. This helped resolve some usability issues for OpenLB.
	\item Traceability. Provide a developer's guide to help orient developers to
	the artifacts, source code, and system architecture so that they can better
	document changes. Top ranked package OpenLB has a developer guide. \wss{How
	is this related to traceability?}
	\item Visibility and Transparency. Summarize the development process that is
	used. Provide information on how new users can contribute. Identify the
	development model by name (waterfall, agile, etc.), if appropriate.  Seven
	of the software packages have some artifacts outlining the general
	development process. Eleven packages have information on how to contribute. 
	\item Visibility and Transparency. Identify the development environment.
	Eight of the 24 software packages identify the development environment.
	\item Visibility and Transparency. Include notes with all releases. Nine of
	the packages include release notes.
	\item Visibility and Transparency. Communicate all changes within the
	development team. This suggestion is based on developer comments.
	\item Visibility and Transparency. Use continuous integration processes and
	tools (Bamboo, Jenkins, and Travis CI). This was done by top ranked packages
	ESPResSo and Ludwig.
	\item Visibility and Transparency. Consider peer review processes to assess
	contributions and ensure the tracking of information. High ranked package
	ESPResSo uses a peer review process for contributions. 
	\item Reproducibility. Test output against automatically calculated or known
	correct results. High ranked package ESPResSo does this.
	\item Reproducibility. Automate the testing of output. Run tests after all
	code changes. High ranked package ESPResSo does this.
	\item Reproducibility. Consider peer review processes and task based
	inspection to assess contributions. High ranked package ESPResSo does this.
	\item Unambiguity. State appropriate fluid dynamics problems that the
	software is designed to model in the documentation, and explicitly state the
	limits of the software. This is done in the ESPResSo user guide.
	\item Unambiguity. The documentation should either explain the underlying
	CFD theories or provide a reference to appropriate resources. This was done
	by several top ranked packages, including ESPResSo, Ludwig, LUMA, and
	OpenLB.
	\item Unambiguity. Consider asking users for feedback on the documentation.
	The developer of pyLBM noted that such feedback would be appreciated.

\end{itemize}

practices mentioned in literature, but not practiced (if any).  Start with the
practices that aren't derived from developer interviews.

\begin{itemize}
	\item Surface Correctness and Verifiability. Use a requirements
	specification document. This is suggested in SCS literature, and several of
	the top ranked packages had such a document or reference to theory manuals.
	A potential template is presented in \citep{smith2005new}. 
	\item Surface Usability. Do not duplicate artifact information. This is
	suggested as good software development practice. Duplicate information is
	difficult to maintain. 
	\item Maintainability. Visibility and Transparency. Reproducibility. Keep artifacts updated.
	This is suggested as good software maintenance practice.
	\item Maintainability. Eliminate code duplication. This is suggested as good
	software development practice. Duplicate code is difficult to maintain.
	\wss{No support for this one or citation, either find or remove it.}
	\item Modifiability. Consider future source code modifiability as early as
	the design stage of development. This is suggested as good software
	development practice. \wss{citation, support, or remove.}
	\item Reusability. Document module interfaces in design and developer
	documentation. This is suggested as good software development practice.
	\wss{citation or support}
	\item Traceability. Update all relevant documentation when a change to the
	software is made. This is suggested as good software development practice.
	\wss{support, cite or remove}
	\item Unambiguity. Documentation must state all technical requirements and
	software dependencies. A missing dependency was a frequent cause of fault
	conditions during this assessment.
	\item Unambiguity. Provide a table of symbols in the developer's guide that
	maps to names used in the source code. This is suggested as good software
	development practice.

\end{itemize}
